CF Registry Analysis

### 2022-12-21 Christine Chan/CF Registry/cf_registry_analysis.qmd
Update cf_registry_analysis.qmd

```{r}
library(table1)
```

>>>>

```{r}
#| include: false
library(tidyverse)
library(table1)
# All data
df = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/Peds Endo/Christine Chan/CF registry data/CFF19_Annualized_Del1.csv",
              na.strings = c("","N/A"))
df = df %>% arrange(eDWID,ReviewYear) 
# For those with CFRD by OGTT, find first visit with diagnosis
first_cfrd = df %>% filter(A_twohour_bloodglucose >= 200) %>% 
  group_by(eDWID) %>% slice_min(ReviewYear) %>% 
  select(eDWID,ReviewYear) %>% rename(first_cfrd = ReviewYear)
df = left_join(df,first_cfrd,by = "eDWID")
df = df %>% group_by(eDWID) %>% 
  mutate(cfrd_ogtt = case_when(
    ReviewYear < first_cfrd ~ "No",
    ReviewYear >= first_cfrd ~ "Yes"
  )) %>%
  ungroup()
df$cfrd_ogtt[is.na(df$cfrd_ogtt)] = "No"
diagnosis = df %>% 
  select(eDWID,ReviewYear,Age_YrEnd,first_cfrd,cfrd_ogtt) %>%
  group_by(eDWID) %>%
  mutate(`Age in 2018` = 2018-(ReviewYear-Age_YrEnd))
```

```{python}
#| @tbl-incidence
import pandas as pd
import numpy as np

diagnosis = r.diagnosis
years = diagnosis["ReviewYear"].unique()
# Loop through years - all ages
cases = []
at_risk = []
incidence = []
for y in years:
  d = diagnosis[diagnosis["ReviewYear"]==y]
  this_year = d.loc[d["cfrd_ogtt"]=="Yes","eDWID"].to_list()
  cases = set(cases).union(this_year)
  new_cases = set(cases).difference(set(this_year))
  at_risk = set(d["eDWID"].to_list()).difference(at_risk)
  incidence.append(round(len(new_cases)/(len(at_risk)/1000),3))
# Loop through years - age < 10
cases = []
at_risk = []
incidence_10 = []
for y in years:
  d = diagnosis[(diagnosis["ReviewYear"]==y) & (diagnosis["Age in 2018"]<10)]
  this_year = d.loc[d["cfrd_ogtt"]=="Yes","eDWID"].to_list()
  cases = set(cases).union(this_year)
  new_cases = set(cases).difference(set(this_year))
  at_risk = set(d["eDWID"].to_list()).difference(at_risk)
  if len(at_risk)==0:
    incidence_10.append(np.nan)
  else:
    incidence_10.append(round(len(new_cases)/(len(at_risk)/1000),3))
# Loop through years - age 10 - 18
cases = []
at_risk = []
incidence_10_18 = []
for y in years:
  d = diagnosis[(diagnosis["ReviewYear"]==y) & (diagnosis["Age in 2018"]>=10) & (diagnosis["Age in 2018"]<=18)]
  this_year = d.loc[d["cfrd_ogtt"]=="Yes","eDWID"].to_list()
  cases = set(cases).union(this_year)
  new_cases = set(cases).difference(set(this_year))
  at_risk = set(d["eDWID"].to_list()).difference(at_risk)
  if len(at_risk)==0:
    incidence_10_18.append(np.nan)
  else:
    incidence_10_18.append(round(len(new_cases)/(len(at_risk)/1000),3))
# Loop through years - age 19 - 30
cases = []
at_risk = []
incidence_19_30 = []
for y in years:
  d = diagnosis[(diagnosis["ReviewYear"]==y) & (diagnosis["Age in 2018"]>=19) & (diagnosis["Age in 2018"]<=30)]
  this_year = d.loc[d["cfrd_ogtt"]=="Yes","eDWID"].to_list()
  cases = set(cases).union(this_year)
  new_cases = set(cases).difference(set(this_year))
  at_risk = set(d["eDWID"].to_list()).difference(at_risk)
  if len(at_risk)==0:
    incidence_19_30.append(np.nan)
  else:
    incidence_19_30.append(round(len(new_cases)/(len(at_risk)/1000),3))
```
